Tables with \textbf{xtable} and \textbf{knitr}

### 2016-11-02 src/ArticleReadyTableGenerate.Rnw
nearly working xtablelist missing double backslashes

<<echo=FALSE, results='asis',cache=FALSE >>=
  for (region in regions) { 
  p_value_table <- matrix(0,nrow = 7,ncol = 9)
  p_val_table_list<-list()
  xtablelist<- list()
  for (side in sides){

@@

  xtab.out <- xtable( as.data.frame(p_value_table_print  ) )
  p_val_table_list[[side]]<- p_value_table_print
  xtablelist[[side]]<-xtab.out

  }
   attr(p_val_table_list, "subheadings") <- paste0("Hemisphere : ",c("Left","Right"))
   xtablelist <- xtableList(p_val_table_list, caption = paste0("Hypothesis Tests based on pooled LCDM statistics for ",region,collapse= ""))
   col.names <- c("KS test","MWU test", "Welch's t-test")
   # Region & \multicolumn{3}{l}{KS test} & \multicolumn{3}{l}{MWU test} & \multicolumn{3}{l}{Welch's t-test}\\
  rowcom <- list()
  rowcom$pos = list(-1)
  rowcom$command = paste0(paste0("Region",paste0(" & \\multicolumn{3}{c}{", col.names , '}', collapse=''),collapse=''), '\\\\')
  #print(addtorow)
  print(xtablelist, add.to.row = rowcom, only.contents=FALSE,
    include.rownames=TRUE, sanitize.colnames.function = simp.colnames,
    type="latex",floating.environment = "sidewaystable")
  }

>>>>

<<echo=FALSE, results='asis',cache=FALSE >>=
  for (region in regions) { 
    p_value_table <- matrix(0,nrow = 7,ncol = 9)
    p_val_table_list <- list()
    xtablelist <- list()
    for (side in sides){

@@

      xtab.out <- xtable( as.data.frame(p_value_table_print  ) )
      p_val_table_list[[side]]<- p_value_table_print
      xtablelist[[side]]<-xtab.out
    }
    attr(p_val_table_list, "subheadings") <- paste0("Hemisphere : ",c("Left","Right"))
    xtablelist <- xtableList(p_val_table_list, caption = paste0("Hypothesis Tests based on pooled LCDM statistics for ",region,collapse= ""))
    col.names <- c("KS test","MWU test", "Welch's t-test")
    # Region & \multicolumn{3}{l}{KS test} & \multicolumn{3}{l}{MWU test} & \multicolumn{3}{l}{Welch's t-test}\\
    rowcom <- list()
    rowcom$pos = list(-1)
    rowcom$command = paste0(paste0("Region",paste0(" & \\\\multicolumn{3}{c}{", col.names , '}', collapse=''),collapse='')," \\\\ " ,collapse="")
    print(rowcom$command)
    xtablelist.out<-print(xtablelist, only.contents=FALSE,
      include.rownames=TRUE, sanitize.colnames.function = simp.colnames,
      type="latex",floating.environment = "sidewaystable", print.results = FALSE)
    second_heading <- "(\\\\begin\\{tabular\\}.*)" 
    xtablelist.out <- gsub( xtablelist.out, pattern = second_heading, perl =  TRUE,fixed=FALSE,
    replacement =  paste0( "\\1", "\n", rowcom$command, collapse = '') )
    cat(xtablelist.out,sep="\n")
  }
